% Content is copyright Wizards of the Coast 2000, used under Open Game License v1.0a
\monsterCard[title=Adult Red Dragon, type={Huge dragon, chaotic evil}, ac=19 (natural armor), hp=256 (19d12+133), speed={40ft, climb 40ft, fly 80ft}, str=27, dex=10, con=25, int=16, wis=13, cha=21, saves={DEX +6, CON +13, WIS +7, CHA +11}, skills={Perception +13, Stealth +6}, damage immunities=fire, senses={Blindsight 60ft, Darkvision 120ft}, languages={Common, Draconic}, cr=17, source={SRD, MM 98},scale=0.8]{
\ability{Legendary Resistance (3/Day)}{If fail a saving throw, can choose to succeed instead.}

\Actions

\ability{Multiattack}{The dragon can use its Frightful Presence. It then makes three attacks: one with its bite and two with its claws.}

\MeleeAttack{Bite}{+14 to hit, reach 10ft, one target.}{19 (2d10+8) piercing damage plus 7 (2d6) fire damage.}

\MeleeAttack{Claw}{+14 to hit, reach 5ft, one target.}{15 (2d6+8) slashing damage.}

\MeleeAttack{Tail}{+14 to hit, reach 15ft, one target.}{17 (2d8+8) bludgeoning damage.}

\ability{Frightful Presence}{Each creature of dragon's choice within 120 feet of dragon and aware of it must succeed on a DC 19 WIS save or become frightened for 1 minute. A creature can repeat the save at the end of each of its turns, ending the effect on itself on a success. If a creature's saving throw is successful or the effect ends for it, the creature is immune to the dragon's Frightful Presence for the next 24 hours.}

\ability{Fire Breath (Recharge 5-6)}{Exhale fire in a 60-foot cone. Each creature in that area makes a DC 21 DEX save, taking 63 (18d6) fire damage on fail or half on a success.}

\LegendaryActions

\ability{Detect}{The dragon makes a Wisdom (Perception) check.}

\ability{Tail Attack}{The dragon makes a tail attack.}

\ability{Wing Attack (Costs 2 Actions)}{The dragon beats its wings. Each creature within 10 feet of the dragon must succeed on a DC 22 DEX save or take 15 (2d6 + 8) bludgeoning damage and be knocked prone. The dragon can then fly up to half its flying speed.}
}